Applying Multi-Core Model Checking to Hardware-Software Partitioning in Embedded Systems

### 2015-09-01 Docs/Paper/LaTex/template.tex
emphasize i.e. and e.g.

In some cases, the time to find a solution using ILP is impractical. Even with the use of powerful computers, a problem can take hours before an optimal solution is reached. If the optimization problem is complex, some heuristics can be used to solve the same problem faster, e.g., those used in the GA~\cite{Rao2009}. The only drawback is that the found solution may not be the global minimum or maximum. Alternatively, tools such as vZ and ESBMC can be used to solve optimization problems so that the global minimum or maximum solution is found. The following sections describe the main features of vZ and ESBMC tools.

@@

%----------------------------------------------
\subsection{OpenMP}
\label{OpenMP}
%----------------------------------------------
The OpenMP is a set of directives for parallel programming that augments C/C$++$ and Fortran languages. OpenMP supports most processor architectures and operating systems, e.g., Solaris, AIX, HP-UX, Linux, Mac OS X, and Windows. OpenMP uses a portable and very robust model that makes easy for programmers to develop parallel applications for a variety of platforms.

@@

An SMT solver is a tool that verifies formula satisfiability based on a set of background theories (e.g., linear arithmetic, bitvectors, and arrays). \textcolor{red}{Z3 is built on the a Davis–Putnam–Logemann–Loveland algorithm together with auxiliary algorithms for solving quantifiers formulas~\cite{Bjorner2014}}. vZ is one of the tools implemented in the SMT solver Z3; its base function is to optimize objective functions, which formulate optimized criteria, within the logical context of constraints.  vZ includes an incremental version of  \textcolor{red}{Maximum Resiliency (MaxRes) ~\cite{Federica2008} to Maximum Satisfiability (MaxSAT)~\cite{NarodytskaN}} and a Simplex to solve numbers without defined patterns. In Vz, MaxSAT is responsible for the restrictions, while OptSMT optimizes linear arithmetic objectives~\cite{Bjorner2015}. Vz provides functions that extend Z3 for solving optimization problems: \textit{maximize}, \textit{minimize}, and \textit{assert-soft}.

@@

Since the second half of the first decade of the 2000s, three main paths have been tracked to improve or to present alternative solutions to the optimization of HW-SW partitioning, i.e., to find the exact solution ~\cite{Mann2007}, to use heuristics to speed up performance time ~\cite{Arato2003}, and hybrid ones ~\cite{Arato2005}.

@@

In terms of SMT-based verification, most work is restricted to present the model, its modification to programming languages (e.g., C/C++ and Java), and the application to multi-thread algorithms or to embedded systems to check for program correctness. In ~\cite{Ramalho2013} it presents a bounded model checker for C++ programs, which is an evolution of dealing with C programs and ~\cite{Cordeiro2012} uses the ESBMC model checker for embedded ANSI-C software. In~\cite{Trindade2015} and~\cite{Trindade2014} it was proven that it is possible to use ESBMC to solve HW-SW partitioning, but in a single core way. There are related studies focused on decreasing the verification time of model checkers by applying Swarm Verification ~\cite{Holzmann2011}, and modifications of internal search engines to support parallelism ~\cite{Holzmann2012}, but there is still the need for initiatives related to parallel SMT solvers ~\cite{Wintersteiger2009}. Recently, the SMT solver Z3 has been extended to pose and solve optimization problems modulo theories ~\cite{Bjorner2015}.

>>>>

In some cases, the time to find a solution using ILP is impractical. Even with the use of powerful computers, a problem can take hours before an optimal solution is reached. If the optimization problem is complex, some heuristics can be used to solve the same problem faster, {\it e.g.}, those used in the GA~\cite{Rao2009}. The only drawback is that the found solution may not be the global minimum or maximum. Alternatively, tools such as vZ and ESBMC can be used to solve optimization problems so that the global minimum or maximum solution is found. The following sections describe the main features of vZ and ESBMC tools.

@@

%----------------------------------------------
\subsection{OpenMP}
\label{OpenMP}
%----------------------------------------------
The OpenMP is a set of directives for parallel programming that augments C/C$++$ and Fortran languages. OpenMP supports most processor architectures and operating systems, {\it e.g.}, Solaris, AIX, HP-UX, Linux, Mac OS X, and Windows. OpenMP uses a portable and very robust model that makes easy for programmers to develop parallel applications for a variety of platforms.

@@

An SMT solver is a tool that verifies formula satisfiability based on a set of background theories ({\it e.g.}, linear arithmetic, bitvectors, and arrays). \textcolor{red}{Z3 is built on the a Davis–Putnam–Logemann–Loveland algorithm together with auxiliary algorithms for solving quantifiers formulas~\cite{Bjorner2014}}. vZ is one of the tools implemented in the SMT solver Z3; its base function is to optimize objective functions, which formulate optimized criteria, within the logical context of constraints.  vZ includes an incremental version of  \textcolor{red}{Maximum Resiliency (MaxRes) ~\cite{Federica2008} to Maximum Satisfiability (MaxSAT)~\cite{NarodytskaN}} and a Simplex to solve numbers without defined patterns. In Vz, MaxSAT is responsible for the restrictions, while OptSMT optimizes linear arithmetic objectives~\cite{Bjorner2015}. Vz provides functions that extend Z3 for solving optimization problems: \textit{maximize}, \textit{minimize}, and \textit{assert-soft}.

@@

Since the second half of the first decade of the 2000s, three main paths have been tracked to improve or to present alternative solutions to the optimization of HW-SW partitioning, {\it i.e.}, to find the exact solution ~\cite{Mann2007}, to use heuristics to speed up performance time ~\cite{Arato2003}, and hybrid ones ~\cite{Arato2005}.

@@

In terms of SMT-based verification, most work is restricted to present the model, its modification to programming languages ({\it e.g.}, C/C++ and Java), and the application to multi-thread algorithms or to embedded systems to check for program correctness. In ~\cite{Ramalho2013} it presents a bounded model checker for C++ programs, which is an evolution of dealing with C programs and ~\cite{Cordeiro2012} uses the ESBMC model checker for embedded ANSI-C software. In~\cite{Trindade2015} and~\cite{Trindade2014} it was proven that it is possible to use ESBMC to solve HW-SW partitioning, but in a single core way. There are related studies focused on decreasing the verification time of model checkers by applying Swarm Verification ~\cite{Holzmann2011}, and modifications of internal search engines to support parallelism ~\cite{Holzmann2012}, but there is still the need for initiatives related to parallel SMT solvers ~\cite{Wintersteiger2009}. Recently, the SMT solver Z3 has been extended to pose and solve optimization problems modulo theories ~\cite{Bjorner2015}.
